Intelligent Reflecting Surface-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design

### 2021-03-15 main.tex
:pencil: Update abstract

	\begin{abstract}
		The performance of Simultaneous Wireless Information and Power Transfer (SWIPT) is severely restricted by the strength of the received Radio-Frequency (RF) signal. To tackle this problem, we introduce a low-power Intelligent Reflecting Surface (IRS) that compensates the propagation loss and boosts the transmission efficiency by a passive beamforming gain. This paper investigates an efficient IRS-aided SWIPT architecture where a multi-carrier multi-antenna Access Point (AP) transmits information and power simultaneously to a single-antenna User Equipment (UE) under the assist of an IRS. Considering energy harvester nonlinearity, we aim to maximize the Rate-Energy (R-E) tradeoff through a joint optimization of the transmit waveform and active beamforming at the AP, the reflection coefficients at the IRS, and the power splitting ratio at the UE. Stationary solutions are achieved by the Alternating Optimization (AO) technique, where the optimal active beamforming is obtained in closed form, the passive beamforming is optimized by the Successive Convex Approximation (SCA) technique, and the waveform and splitting ratio are optimized by the Geometric Programming (GP) technique. Although practical IRS is limited to Frequency-Flat (FF) reflection, results demonstrate significant benefits of the proposed architecture based on a joint waveform and beamforming design to enlarge the R-E region of IRS-aided SWIPT.
	\end{abstract}

	\begin{IEEEkeywords}
		Simultaneous wireless information and power transfer, intelligent reflecting surface, waveform design, active and passive beamforming.
	\end{IEEEkeywords}

>>>>

	\begin{abstract}
		The performance of Simultaneous Wireless Information and Power Transfer (SWIPT) is mainly constrained by the received Radio-Frequency (RF) signal strength. To tackle this problem, we introduce an Intelligent Reflecting Surface (IRS) to compensate the propagation loss and boost the transmission efficiency. This paper proposes a novel IRS-aided SWIPT system where a multi-carrier multi-antenna Access Point (AP) transmits information and power simultaneously to a single-antenna User Equipment (UE) under the assist of an IRS. Considering energy harvester nonlinearity and practical transceiving strategies, we characterize the achievable Rate-Energy (R-E) region through a joint design of waveform, active and passive beamforming based on the Channel State Information at the Transmitter (CSIT). This non-convex problem is then solved by the Alternating Optimization (AO) method, where the active precoder is obtained in a closed form, the passive beamformer is optimized by the Successive Convex Approximation (SCA) approach, and the waveform is designed by the Geometric Programming (GP) technique. Since the complexity of the GP-based algorithm scales exponentially with the number of subbands, we also propose two low-complexity adaptive waveform design to facilitate practical SWIPT implementation. Simulation results show considerable R-E gain over benchmark schemes and demonstrate the importance of accounting harvester nonlinearity in the passive beamforming design.
	\end{abstract}

	\begin{IEEEkeywords}
		Simultaneous wireless information and power transfer, intelligent reflecting surface, waveform design, beamforming design, energy harvester nonlinearity.
	\end{IEEEkeywords}
